\`\`Dr. Tustison (UVA) presentation\'\

### 2016-07-17 evaluation/antsvfreesurfer2.Rmd
ENH:  Remove slides.

* Sandy, Brian, and <span style="color:red;">DiReCT</span>
    + used other tools such as FMRIB Automated Segmentation Tool (FAST)
    + `KellySlater.cxx`
* pipedream scripts "adequate for Penn data."
* `KellyKapowski.cxx` and `antsCorticalThickness.sh`
* _"Let's evaluate on open data."_
* and, eventually, _"Let's compare with FreeSurfer."_
-->

@@

<!--
* Public data sets (IXI, NKI, OASIS, MMRR)
* $>$ 1200 subjects, age 4 to over 94 years old
-->

>>>>

* Sandy, Brian, and <span style="color:red;">DiReCT</span>
    + used other tools such as FMRIB Automated Segmentation Tool (FAST)
    + `KellySlater.cxx`
* pipedream scripts "adequate for Penn data."
* `KellyKapowski.cxx` and `antsCorticalThickness.sh`
* _"Let's evaluate on open data."_
* and, eventually, _"Let's compare with FreeSurfer."_

@@

* Public data sets (IXI, NKI, OASIS, MMRR)
* $>$ 1200 subjects, age 4 to over 94 years old
-->

### 2016-07-17 ibm.Rmd
ENH:  Remove slides.

<!--- A great opportunity to showcase a [new SyN variant](http://www.ncbi.nlm.nih.gov/pubmed/24409140) -->
# ANTs lineage

## Image mapping and perception: 1877

Francis Galton: _Can we see criminality in the face?_

![](./figures/galton.png)

_What about syphilis, mental illness?_

<!--
Notes:
* Use of "composite portraiture" and what he called "eugenics"
* Can we see criminality, mental illness, syphilis, and others in facial features?
* Despite the obvious prejudices driving his research, he was a pioneer.
-->

##

![](./background/figures/FrancisGalton2.jpg)
-->

<!--
Notes:
* Another example where he has manually categorized facial features and try to combine them
* Did not find much---composite tends to blend away to normality.
-->

##  Speaking of criminality...

_Can we say anything about the U.S. Congress?_

![](./background/figures/congressPersons.png)

__Maybe they should have used [ANTs](https://github.com/ntustison/CongressionalFaceTemplates)?__

<!--
Notes:
-->

##  Image mapping & biology:  1917

D'Arcy Thompson: _Comparison of related forms_

![](./figures/dthompson.png)
-->

<!--
Notes:
* Book: On Growth and Form
* Descriptive
* "This book of mine has little need of preface, for indeed it is 'all preface' from beginning to end."
-->

## Image mapping & biology: Current
<BR><BR>
_Look where we are now!_
<BR><BR>
![](./background/figures/r16xr85.png)

<!--
## ANTs family tree

![](./figures/lineage.jpg)
-->

<!--
References: @Horn1981, @Gee1993, @Grenander1993, @Thompson2001, @Miller2002, @Shen2002, @Arnold2014, @Thirion1998, @Rueckert1999, @Fischl2012, @Ashburner2012
-->

<!--
## Initial scope

![](./figures/ants_initial_scope.png)
-->

<!--
Notes:
* Brian work with Murray Grossman
* First registration paper
  - WBIR submission
  - FEM registraiton using B-spline basis functions.
  - "yeah, that registration is not that good---Jim would not like it."
-->

@@

_So how does ATITH compare with ANTs, FS?_
-->
## Prediction from cortical thickness data

>>>>

<!--- A great opportunity to showcase a [new SyN variant](http://www.ncbi.nlm.nih.gov/pubmed/24409140) -->

@@

_So how does ATITH compare with ANTs, FS?_
